\section{\huge{Developer usage}}

\subsection{Deployment on the raspberry}
\begin{enumerate}
    \item Connect the raspberry to the internet.
    \item Install NodeJs if it is not installed.
    \item Clone the repository.
    \item Open the terminal in the root directory of the repository.
    \item Execute npm i.
    \item Execute npm run start.
\end{enumerate}

\subsection{Changing the server port or the mongodb uri}
\begin{enumerate}
    \item Open the file config.json.
    \item Set the property PORT as needed.
    \item Set the property of the object MONGO as needed.
\end{enumerate}

\subsection{Changing something in the frontend}
\begin{enumerate}
    \item Open the terminal in the directory vuejs of the repository.
    \item Execute npm i.
    \item Make changes to the frontend source code.
    \item See changes by executing npm run serve and open a browser in http://IP:8080. Start the server if backend api are needed.
    \item Open the terminal in the root directory of the repository.
    \item Execute npm run build:frontend.
    \item Execute npm run start to start the server.
\end{enumerate}

\subsection{Changing the api hostname in the frontend}
\begin{enumerate}
    \item Open the file vuejs/src/config.json of this repository.
    \item Change the host and the port properties as needed.
    \item Open the terminal in the root directory of this repository.
    \item Execute npm run build:frontend.
    \item Execute npm run start to start the server.
\end{enumerate}

\subsection{Automatize with SystemCtl}
On the Raspberry runs Linux Ubuntu. This means that systemctl is available.
To make the exporter run on boot:
\begin{enumerate}
    \item Open a terminal.
    \item Go to the /etc/systemd/system folder.
    \item Create a file by executing touch exporter.service.
    \item Copy this code into that file.
        \begin{alltt}
            [Unit]
            Description=Eagle-TRT telemetry exporter webapp
            Wants=mongodb.service
            After=mongodb.service
            StartLimitIntervalSec=0
            [Service]
            Type=simple
            Restart=always
            RestartSec=5
            User=ubuntu
            ExecStart=/usr/bin/node /home/ubuntu/eagletrt-telemetria-exporter/main.js
            WorkingDirectory=/home/ubuntu/eagletrt-telemetria-exporter
            [Install]
            WantedBy=multi-user.target
        \end{alltt}
    \item Execute sudo systemctl daemon-reload to make the changes effective.
    \item Execute sudo systemctl start exporter. The exporter should start running at this step.
    \item Execute sudo systemctl enable exporter to make the exporter start on boot.
\end{enumerate}